### 2016-09-01 forgerard.tex
Put together writeup

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\beta_{X}$
&
$0.0335^{0.0031}_{-0.0031}$
&
$0.0267^{0.0025}_{-0.0026}$
&
$0.0266^{0.0022}_{-0.0022}$
&
$0.0214^{0.0019}_{-0.0019}$
&
$0.0200^{0.0018}_{-0.0017}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$R_{X}$
&
$4.8715^{0.4826}_{-0.4296}$
&
$3.9642^{0.3953}_{-0.3528}$
&
$2.9644^{0.3118}_{-0.2801}$
&
$2.2869^{0.2559}_{-0.2322}$
&
$1.6395^{0.2112}_{-0.1939}$
\\
$R_{\delta X}$
&
$-2.6978^{1.3200}_{-2.4424}$
&
$-3.4586^{1.2929}_{-2.6501}$
&
$-4.4569^{1.4269}_{-3.1109}$
&
$-4.2020^{1.3152}_{-2.8944}$
&
$-3.8012^{1.2005}_{-2.6141}$
\\
$\sigma_{X}$
&
$0.0592^{0.0124}_{-0.0112}$
&
$0.0315^{0.0069}_{-0.0073}$
&
$0.0201^{0.0041}_{-0.0055}$
&
$0.0127^{0.0069}_{-0.0079}$
&
$0.0425^{0.0051}_{-0.0044}$
\\
\hline
\end{tabular}
\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model \label{global:tab}}
\end{table}

@@

We find a small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
magnitudes.  All bands show larger and significant non-zero values for $\beta$.  This confirms the part of our hypothesis that spectral indicators
are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.

The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Our measurement of
$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
the $R_X$ are consistent with the  $R_V=3.1$ CCM model (assuming we are using
SNf synthetic magnitudes).  The uncertainties in the 5 measurements
of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are also consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$.
   \label{rx:fig}}
\end{figure}

@@

The best-fit distribution for $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can get close to zero, resulting in the
elongated tail in negative  $R_{\rho X}$.
All values are inconsistent with zero and negative: a color excess in $B-V$ produces a brightening of the supernova.
The smallest (most negative) value is for the $V$ band with  values increasing in both bluer and redder directions; an
example consequence is that
a reddening in $B-V$ comes with a blueing in $V-R$.
These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail and so may be indicative of
more complicated underlying physics.

The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\rho(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.074 mag while that of $E_\rho(B-V)$ is 0.019 mag.
Both distributions are non-Gaussian extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of $E(B-V) =(\gamma_1-\gamma_2)k$ and
   $E_\rho(B-V) = (\delta_1-\delta_2)D$.
   \label{ebv:fig}}
\end{figure}

Let us conflate the two separate color effects into a single effective extinction with
\begin{equation}
R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}.
\end{equation}
The distribution for $R_{V,eff}$ is shown in Figure~\ref{rveff:fig}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/rveff.pdf}
   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}$,
   \label{rveff:fig}}
\end{figure}
with  $R_{V,eff}  = 1.52 \pm 0.24$.  This may explain why previous analyses have produced low $R_V$ values.

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion is quite small, ranging from 0.01 to 0.06 mag.

@@

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\alpha_X/\alpha_2-1$
&
$   2.0^{   1.3}_{  -0.6}$
&
$   0.0^{   0.1}_{  -0.2}$
&
$   0.0^{   0.0}_{   0.0}$
&
$   0.0^{   0.2}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.033^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.002}_{-0.002}$
&
$ 0.021^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
\\
$\beta_X/\beta_2-1$
&
$  0.26^{  0.05}_{ -0.05}$
&
$  0.00^{  0.03}_{ -0.03}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.25^{  0.03}_{ -0.03}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$\eta_X/\eta_2-1$
&
$  0.26^{  0.65}_{ -0.65}$
&
$ -0.09^{  0.53}_{ -0.55}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.08^{  0.24}_{ -0.21}$
&
$ -0.57^{  0.51}_{ -0.59}$
\\
$R_{X}$
&
$  4.87^{  0.48}_{ -0.43}$
&
$  3.96^{  0.40}_{ -0.35}$
&
$  2.96^{  0.31}_{ -0.28}$
&
$  2.29^{  0.26}_{ -0.23}$
&
$  1.64^{  0.21}_{ -0.19}$
\\
$R_{\delta X}$
&
$ -2.70^{  1.32}_{ -2.44}$
&
$ -3.46^{  1.29}_{ -2.65}$
&
$ -4.46^{  1.43}_{ -3.11}$
&
$ -4.20^{  1.32}_{ -2.89}$
&
$ -3.80^{  1.20}_{ -2.61}$
\\
$\sigma_{X}$
&
$ 0.059^{ 0.012}_{-0.011}$
&
$ 0.031^{ 0.007}_{-0.007}$
&
$ 0.020^{ 0.004}_{-0.006}$
&
$ 0.013^{ 0.007}_{-0.008}$
&
$ 0.043^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% Intervals for Global Fit Parameters  \label{global:tab}}
\end{table}

@@

We find a small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
magnitudes.  All bands show larger and significant non-zero values for $\beta$.  This confirms the part of our hypothesis that spectral indicators
are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.
The effect in color can be seen in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$.
Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically, while
$v_{Si}$ does not have a significant affect on colors.

The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
shows the expectation of CCM dust, plotted together with our measurements of
$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the central wavelength of the synthetic bands.
the $R_X$ are consistent with the  $R_V=3.1$ CCM model (assuming we are using
SNf synthetic magnitudes).  The uncertainties in the 5 measurements
of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are also consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
   \label{rx:fig}}
\end{figure}

@@

The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can get close to zero, resulting in the
elongated tail in negative  $R_{\delta X}$.
All values are inconsistent with zero and negative: a color excess in $B-V$ produces a brightening of the supernova.
The smallest (most negative) value is $R_{\delta V}$  with  values increasing in both bluer and redder directions; a consequence
of which is that
a reddening in $B-V$ comes with a blueing in $V-R$.
These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
more complicated underlying supernova physics.

The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
The range of $B-V$ colors is almost 4 times larger for the external contribution:
extreme colors can thus be attributed to the external source. 
Both distributions are non-Gaussian extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of $E(B-V) =(\gamma_1-\gamma_2)k$ and
   $E_\delta(B-V) = (\delta_1-\delta_2)D$.
   \label{ebv:fig}}
\end{figure}

The two separate color effects are conflated into a combined color excess with a single effective extinction behavior
\begin{equation}
R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}.
\end{equation}
The distribution for $R_{V,eff}$ is shown in Figure~\ref{rveff:fig}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/rveff.pdf}
   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
   \label{rveff:fig}}
\end{figure}
and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
Rerunning the posterior calculation with initial conditions for $\gamma$  near $R_{X,eff}$ reproduced the original results, indicating that
the effective and true $R$ values are not separated by local posterior extrema.

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: the distributions (for all Monte Carlo chain links for all supernovae) are shown in Figure~\ref{perobject:fig}.
There is a core distribution within the supernova parameter-space, with around ten objects that live on the outskirts of that
distribution.  Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
Otherwise the distribution in $EW_{Ca}$--$v_{Si}$ space is the view that
shows the most outliers.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are shown in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
$EW_{Si}$--$v_{Si}$, which are statistics that describe the same spectral feature.
External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
